A Spatial AR System for Wide-area Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-07-09 paper/elsarticle/elsarticle-template.tex
paper

\begin{figure}
    \centering
    %\subfloat[\centering Initial virtual projector.]{{\includegraphics[height=3.25cm]{images/1.png} }}
    %\qquad
    \subfloat[\centering Virtual camera.]{{\includegraphics[height=4.5cm]{images/2.png}}}
    \qquad
    \subfloat[\centering Virtual projector.]{{\includegraphics[height=4.5cm]{images/3.png}}}
    \caption{Obtaining the virtual projector. (a) The virtual camera is obtained by rotating the camera about its center of projection such that its optical axis be made parallel with the normal vector of the scene plane. (b) The virtual projector is obtained by (i) rotating the projector about the point of intersection of its optical axis with the scene plane such that its optical axis be made parallel with the scene plane's normal, (ii) rotating the $X$- and $Y$-axes to render them parallel with those of the virtual camera, and (iii) translating to achieve the desired projected image dimensions.}
    \label{fig:virtualproj}
\end{figure}

\paragraph{Virtual projector} The placement of the virtual projector determines from which pose the image to be projected is to \textit{appear} to have been projected. This placement is produced according to a small handful of steps. First, we (i) intersect the scene plane with the optical axis (i.e., the ray from the projector's center of projection through the center of the image plane); next, we (ii) rotate the projector's placement about that point of intersection, aligning the optical axis with the scene plane's normal vector and giving an initial virtual projector. Separately, we (iii) rotate the camera about its center of projection to align its optical axis with the normal vector of the scene plane, giving a virtual camera likewise facing directly\footnote{A physical camera placed to face downwards is likely to not face downwards precisely; in contrast, the virtual camera's optical axis is aligned exactly with the scene plane's normal vector, rendering it fronto-parallel with respect to the scene plane.} downwards to the scene plane. Finally, we (iv) rotate the $X$- and $Y$-axes of the initial virtual projector with those of the virtual camera, which gives the virtual projector. The virtual projector is thus rendered fronto-parallel with the scene plane, enabling projection to the scene plane absent of projective distortions. Optionally, we additionally adjust the height above the scene plane of the virtual projector, in order to satisfy desired projected image dimensions provided in metric units.

>>>>

\begin{figure}
    \centering
    \subfloat[\centering Oblique view.]{{\includegraphics[height=4.25cm]{images/3.png}}}
    \qquad
    \subfloat[\centering Downwards view.]{{\includegraphics[height=4.25cm]{images/3_above3.png}}}
    \caption{The virtual camera is obtained by rotating the camera (top left, black) about its center of projection such that its optical axis be made parallel with the normal vector of the scene plane. The virtual projector is obtained by (i) rotating the projector (bottom left, black) about the point of intersection of its optical axis with the scene plane such that its optical axis be made parallel with the scene plane's normal vector, (ii) rotating the $X$- and $Y$-axes to render them parallel with those of the virtual camera, and (iii) optionally translating along the normal direction to achieve the desired projected image dimensions.} %The virtual projector is thus rendered fronto-parallel with the ground plane and axially aligned with the virtual camera.
    \label{fig:virtualproj}
\end{figure}

\paragraph{Virtual projector} The placement of the virtual projector determines from which pose the image to be projected is to \textit{appear} to have been projected. This placement is produced according to a small handful of steps. First, we (i) rotate the camera about its center of projection to align its optical axis with the normal vector of the scene plane, giving a virtual camera likewise facing directly\footnote{A physical camera placed to face downwards is likely to not face downwards precisely; in contrast, the virtual camera's optical axis is aligned exactly with the scene plane's normal vector, rendering it fronto-parallel with respect to the scene plane.} downwards to the scene plane (cf.\ Figure~\ref{fig:virtualproj}(a)). Next, we (ii) intersect the scene plane with the optical axis (i.e., the ray from the projector's center of projection through the center of the image plane); then, we (iii) rotate the projector's placement about that point of intersection, aligning the optical axis with the scene plane's normal vector and giving an initial virtual projector. Finally, we (iv) rotate the $X$- and $Y$-axes of the initial virtual projector with those of the virtual camera, which gives the virtual projector (cf.\ Figure~\ref{fig:virtualproj}(b)). The virtual projector is thus rendered fronto-parallel with the scene plane, enabling projection to the scene plane absent of projective distortions. Optionally, we additionally adjust the height above the scene plane of the virtual projector, in order to satisfy desired projected image dimensions provided in metric units.
